---
title: "vignette_pslasso"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette_pslasso}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Import the package *pslassoR*

```{r setup}
library(pslassoR)
```

- Simulate a design matrix X with 100 rows and 300 column. Here we set the covariance matrix of X is exchangeble type. 

- And a sparse coefficient vector is generated with K = 1. 

- Generate a binary response vector y based on simulated X and $\beta$.

```{r}

set.seed(1)

n = 100

P = 300

K = 1 # K measures sparsity

beta = 5*beta.coef(K, P)

X = pslassoR::Auto(0.2, P = P, N = n)

expit = function(x){
  return(exp(x)/(1 + exp(x)))
}

y = X %*% beta + rnorm(n)

#y = rbinom(n,size = 1, prob = expit(X %*% beta))

```

Then we can fit this model with precision lasso method and get corresponding coefficients estimation.  

```{r}

T.Beta = (abs(beta) > 0)

Beta = PSlasso(X, y, logistic = F)

#Beta = glmreg(X,y,logistic = T, method = "lasso")

plot(Beta)

```

To repeat the simulation results, you can run the codes 
```{r, eval= F}

type.vec = c("Auto", "block", "exch")
rho.vec = c(0.2, 0.8)
n.vec = c(100, 400)
K.vec = c(5,20,40)
result = multipleSimulation(type.vec = type.vec,
                            rho.vec = rho.vec,
                            n.vec = n.vec,
                            K.vec = K.vec,
                            mccores = 1)

```

For the results on the runing time for simulation, you can check

```{r, eval = F}
library(parallel)

Test = function(K, node){
  op = mclapply(1:K, Simulation, n =100, K = 20, rho = 0.2, type = "block", mc.cores=node)
}


result1 = microbenchmark(Simulation(1,n =100, K = 20, rho = 0.2, type = "block") , times = 100)

library(microbenchmark)
result2 =  microbenchmark(Test(K = 10,node = 1),Test(K = 10,node = 2), Test(K = 10,node = 4), times = 10)

```
